Associative Data Structures for Website Filtering

### 2014-04-17 paper/paper.tex
Added references.

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}

@@

    In technical terms, we are interested in the best data structure for associating many URLs with
    their respective permissions, be it whitelisted or blacklisted for certain users.  We have
    chosen to compare the performance of the binary search tree, the hash table, and the skip list, as
    these are commonly employed in practice.  It is of particular interest how each data structure
    will scale as the number of elements rises.  We have thus chosen for our main research question
    the following:
    % Guys, did you notice we did absolutely nothing about predicting this?

@@

    We used C++ implementations of the data structures involved, and also used the language for our
    measuring code.  We chose C++ as it is an industry standard\footnote{ref}, provides the
    necessary tools, and does not carry the risk of garbage collection pauses or effects due to
    ``warming-up time''.

    The following is an overview of our implementation.  More specific details can be found in the
    source code.\footnote{cite code here}

@@

    With C++ as the implementation language, we chose libstdc++'s implementations of the standard
    class templates \texttt{std::map} and \texttt{std::unordered\_map} for the binary search tree
    and the hash table respectively.  As the C++ standard library does not contain a skip
    list\footnote{reference to the standard here}, we used an open-source third party library,
    \texttt{CSSkipList}\footnote{reference to library home page here}.  We also used libstdc++'s
    implementation of \texttt{std::string} for our string handling\footnote{specify?}needs.

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{url}
\usepackage[pdftex]{graphicx}

@@

    In technical terms, we are interested in the best data structure for associating many URLs with
    their respective permissions, be it whitelisted or blacklisted for certain users.  We have
    chosen to compare the performance of the binary search tree, the hash table, and the skip list
    data structures~\cite{Algorithms} as these are commonly employed in practice.  It is of
    particular interest how each data structure will scale as the number of elements rises.  We have
    thus chosen for our main research question the following:
    % Guys, did you notice we did absolutely nothing about predicting this?

@@

    We used C++ implementations of the data structures involved, and also used the language for our
    measuring code.  We chose C++ as it is an industry standard~\cite{TC++PL}, provides the
    necessary tools, and does not carry the risk of garbage collection pauses or effects due to
    ``warming-up time''.

    The following is an overview of our implementation.  More specific details can be found in the
    source code~\cite{OurCode}.

@@

    With C++ as the implementation language, we chose \texttt{libstdc++}'s implementations of the standard
    class templates \texttt{std::map} and \texttt{std::unordered\_map} for the binary search tree
    and the hash table respectively~\cite{C++11}.  As the C++ standard library does not contain a
    skip list, we used an open-source third party library, \texttt{CSSkipList}~\cite{CSSkipList}.
    We also used \texttt{libstdc++}'s implementation of \texttt{std::string} for the storage of
    domains and full paths.
